FATE summary results

### 2019-09-04 paper draft.Rmd
New plotting for GOA biology

pdf("goa.climate.loadings.pdf", 6,6)
print(plot_loadings(rotated, names = new.names, threshold=0.8))
dev.off()

@@

```{r, echo=F}
# trends
# pdf("goa.climate.trends.pdf", 6,6)
# print(plot_trends(rotated, years = as.numeric(colnames(Y))))
# dev.off()
```

@@

# loadings
pdf("goa.biol.loadings.pdf", 6, 6)
print(plot_loadings(rotated, names = new.names, threshold=0.9))
dev.off()
```

pdf("goa.biol.trend.pdf", 6,6)
print(plot_trends(rotated, years = as.numeric(colnames(Y))))
dev.off()
```

>>>>

@@

```{r, echo=F}
# trends
plot.trend <- data.frame(year=1972:2017, trend=as.vector(rotated$trends_mean),
                         lo=as.vector(rotated$trends_lower),
                         hi=as.vector(rotated$trends_upper))

png("combined GOA climate loading and trend plot.png", 8, 4, units = "in", res=300)

dev.off()
```

@@

plot.a <- ggplot(plot.load, aes(key, value)) +
  theme_bw() +
  geom_violin(fill=cb[3]) +
  geom_hline(yintercept = 0) +
  theme(axis.title.y = element_blank()) + ylab("Loading") +
  coord_flip() +
  ggtitle("a) Loadings")
```

```{r, echo=F}
# trends
plot.trend <- data.frame(year=1972:2017, trend=as.vector(rotated$trends_mean),
                         lo=as.vector(rotated$trends_lower),
                         hi=as.vector(rotated$trends_upper))

png("combined GOA climate loading and trend plot.png", 8, 4, units = "in", res=300)

dev.off()
```

```{r, echo=F}
# look at rolling correlations between fitted and observed values, as in Ecology paper
modelfit <- GOA.biol$best_model

  res.df$year <-  rep(1972:2017, each=n_ts)

    par(mfrow=c(2,4))
    for(i in 1:length(index)){
     # i <- 1
      temp <- res.df %>%
        filter(ID==index[i])
      temp <- na.omit(temp)
      acf(temp$mean.res, main=index[i]) 
    }
# using 25-yr rolling windows!

# remove correlations with < 10 obs
dfa.cor <- dfa.cor %>%
  filter(n.cor>=10)
 dfa.cor$window <- as.factor(dfa.cor$window)

dfa.cor <- na.omit(dfa.cor)

ggsave("goa biology dfa correlations 11 15 25 year windows.png", height = 4, width=6, units="in")

ggsave("goa biology dfa correlations 15 year windows.png", height = 4, width=6, units="in")

ggsave("goa biology dfa correlations 25 year windows.png", height = 5.5, width=8, units="in")
